### 2019-03-19 4_implementation.tex

TensorFlow~\cite{TensorFlow15} is a programming system intended for
the executing deep learning workloads, widely used in industrial data
center applications. Although TensorFlow's high-level API exposes
concepts specific to machine learning, internally TensorFlow is
implemented as a task graph execution engine, making it a good fit for
Task Bench and one of the shorter implementations at only 88 lines.

Our Task Bench implementation in TensorFlow works by defining a custom
operator, which represents the execution of one task. We then use
TensorFlow APIs to instantiate the custom operator for each point in
the task graph and connect the task dependencies with the TensorFlow
API.

>>>>

TensorFlow~\cite{TensorFlow15} is a programming system intended for
the executing deep learning workloads, widely used in industrial data
center applications. Although TensorFlow's high-level API exposes
concepts specific to machine learning, internally TensorFlow is
implemented as a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs are written by creating nodes in the
task graph, and then connecting these nodes with edges to implement
the desired dataflow. Task graphs are composed in a high-level
language such as Python, but then serialized and run by an efficient
execution engine written in C++.

Our Task Bench implementation in TensorFlow works by defining a custom
operator, which we instantiate for each point in the task graph. We
then define dataflow edges to correspond to the task dependencies.
